### 2016-07-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
reference added for PRISMA
added figures and edited references

\subsection*{Background:  {\em The nature of creativity}} \label{background}

@@

The 30 papers selected for the creativity corpus are listed in Fig. 1a. %\ref{S1a_Fig}.

@@

The non-creativity corpus papers were selected by a literature search retrieving, for each paper in the creativity corpus, the two most-cited papers in the same academic discipline (as categorised by  {\em Scopus}) and published in the same year, that did not contain any words with the prefix {\em creat\/} (i.e. {\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on). \textbf{In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.}

@@

@@

\subsection*{S1 Fig}\label{S1_Fig}
{\bf The 30 papers that make up the Creativity Corpus} 
%\begin{figure}
%\caption{The 30 papers that make up the Creativity Corpus}
% REMOVE IMAGES FROM SUBMITTED VERSION
%\includegraphics[width=\textwidth]{images/papersImage}
%\label{S1_Fig}
%\end{figure}

@@

>>>>

\subsection*{Background:  The nature of creativity} \label{background}

@@

The 30 papers selected for the creativity corpus are listed in Fig. 1a. %\ref{S1a_Fig}. 
\textbf{The search strategy used to select papers for this corpus is illustrated in a PRISMA \cite{prisma09} flow diagram, in Fig. 0a.} %\ref{S0a_Fig}.

@@

The non-creativity corpus papers were selected by a literature search retrieving, for each paper in the creativity corpus, the two most-cited papers in the same academic discipline (as categorised by  {\em Scopus}) and published in the same year, that did not contain any words with the prefix {\em creat\/} (i.e. {\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on). \textbf{In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes. The search strategy used to select papers for this non-creativity corpus is illustrated in a second PRISMA \cite{prisma09} flow diagram, in Fig. 0b. %\ref{S0b_Fig}. 
}

@@

\subsection*{S0a Fig}\label{S0a_Fig}
{\bf A flow diagram describing the search strategy used to identify papers for the creativity corpus} 
%\begin{figure}
%\caption{ A flow diagram describing the search strategy used to identify papers for the creativity corpus}
% REMOVE IMAGES FROM SUBMITTED VERSION
%\includegraphics[width=\textwidth]{images/PRISMAcc}
%\label{S0a_Fig}
%\end{figure}

\subsection*{S0b Fig}\label{S0b_Fig}
{\bf A flow diagram describing the search strategy used to identify papers for the non-creativity corpus} 
%\begin{figure}
%\caption{ A flow diagram describing the search strategy used to identify papers for the non-creativity corpus}
% REMOVE IMAGES FROM SUBMITTED VERSION
%\includegraphics[width=\textwidth]{images/PRISMAncc}
%\label{S0b_Fig}
%\end{figure}

@@

@@

\subsection*{S2 Fig}\label{S2_Fig}
{\bf Word pairwise similarity data visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). } 
%\begin{figure}
%\caption{Word pairwise similarity data visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). }
% REMOVE IMAGES FROM SUBMITTED VERSION
%\includegraphics[width=\textwidth]{images/conceptIdea}
%\label{S2_Fig}
%\end{figure}
